The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-27 dit-paper_ieee.tex
knuth ref + clearer contribution
Added require to Algo Modified Gauss Algorithm
hotfix

	\subsection{Solving the modular system}
		A sketch of the construction algorithm to compute $t_d$ can be found in
		Algorithm~\ref{alg:algoCRP} (note that $x^{-1} \; (mod \; y)$ means the
		modular inverse of $x$ in the naturals modulo $y$). The congruences must
		first be modified in order to obtain pairwise coprime moduli. Each $n_i$
		is factored into prime powers $p^{k_1}_1 p^{k_2}_2 \cdots p^{k_m}_m = n_i$
		with $k_j$ the highest integer s.t. $p^{k_j}_j$ divides $n_i \; \forall j
		\; \mid 1 \leqslant j \leqslant m$. Each original constraint $t_d \equiv x_i
		\; (mod \; n_i)$ is replaced by the equivalent set
		\begin{equation*}
			\begin{split}
				t_d \equiv x_i 	& \; (mod \; p^{k_1}_1) \\
				t_d \equiv x_i 	& \; (mod \; p^{k_2}_2) \\
								& \vdots \\
				t_d \equiv x_i 	& \; (mod \; p^{k_m}_m) \\
			\end{split}
		\end{equation*}
		This operation (later called constraint \emph{factorisation}) might create
		duplicate constraints, which are removed.
		As shown in \cite{knuth1969art}, the resulting system can be solved using
		Algorithm~\ref{alg:algoCRP}. For ease of reading, we call $C$ the set of
		resulting constraints $c$ each written $t_d \equiv x_c \; (mod \;
		p_c)$.

@@

		%TODO change algo 2 with respect to explanation of coprime n_i

		Algorithm~\ref{alg:algoCRP} finds one DIT given one combination of $a_i$
		values. However using it in practice is very inefficient as there are
		exponentially many different combinations of $a_i$ values in the number of
		tasks (the cartesian product of all the $A_i$ sets), and resolving
		exponentially many CRP instances is prohibitively slow.
		A faster method for finding the FPDIT consists in merging all these CRP
		instances into one problem (finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
		results are shared between instances. The first part consisting in splitting
		all constraints into sets of constraints with prime power moduli is slightly
		different. We define for each task $\tau_i$ and $a_j \in A_i$ :
		$C_{ij}$ is the set of constraints resulting from the factorisation of $t_d
		\equiv a_j+O_i \; (mod \; n_i)$ of the form $t_d \equiv x_c
		\; (mod \; p_c)$ if named $c$. We define $C = \bigcup\limits_{\tau_i \in \tau,
		a_j \in A_i}{C_{ij}}$, $P$ the set of all $p_c$ values appearing in
		constraints of $C$ and $C_{p}$ the subset of $C$ containing all constraints
		$c$ with $p_c = p$.

>>>>

	\subsection{Solving the modular system}
		A sketch of the construction algorithm to compute $t_d$ can be found in
		Algorithm~\ref{alg:algoCRP} (note that $x^{-1} \; (mod \; y)$ means the
		modular inverse of $x$ in the naturals modulo $y$). The congruences must
		first be modified in order to obtain pairwise coprime moduli. Each $n_i$
		is factored into prime powers $p^{k_1}_1 p^{k_2}_2 \cdots p^{k_m}_m = n_i$
		with $k_j$ the highest integer s.t. $p^{k_j}_j$ divides $n_i \; \forall j
		\; \mid 1 \leqslant j \leqslant m$. Each original constraint $t_d \equiv x_i
		\; (mod \; n_i)$ is replaced by the equivalent set \cite{knuth1969art}
		\begin{equation*}
			\begin{split}
				t_d \equiv x_i 	& \; (mod \; p^{k_1}_1) \\
				t_d \equiv x_i 	& \; (mod \; p^{k_2}_2) \\
								& \vdots \\
				t_d \equiv x_i 	& \; (mod \; p^{k_m}_m) \\
			\end{split}
		\end{equation*}
		This operation (later called constraint \emph{factorisation}) might create
		duplicate constraints, which are removed.
		As shown in \cite{knuth1969art}, the resulting system can be solved using
		Algorithm~\ref{alg:algoCRP}. For ease of reading, we call $C$ the set of
		resulting constraints $c$ each written $t_d \equiv x_c \; (mod \;
		p_c)$.

@@

		Algorithm~\ref{alg:algoCRP} finds one DIT given one combination of $a_i$
		values. However using it in practice is very inefficient as there are
		exponentially many different combinations of $a_i$ values in the number of
		tasks (the cartesian product of all the $A_i$ sets), and resolving
		exponentially many CRP instances is prohibitively slow.
		In this paper a faster method for finding the FPDIT is proposed. It consists
		in merging all these CRP instances into one problem (finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
		results are shared between instances. The first part consisting in splitting
		all constraints into sets of constraints with prime power moduli is slightly
		different. We define for each task $\tau_i$ and $a_j \in A_i$ :
		$D_{ij}$ the set of constraints $c$ of the form $t_d \equiv x_c
		\; (mod \; p_c)$ resulting from the factorisation of $t_d
		\equiv a_j+O_i \; (mod \; n_i)$. We define $C = \bigcup\limits_{\tau_i \in \tau,
		a_j \in A_i}{C_{ij}}$, $P$ the set of all $p_c$ values appearing in
		constraints of $C$ and $C_{p}$ the subset of $C$ containing all constraints
		$c$ with $p_c = p$.
